---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggprism)
```

```{r}
one_percent_model <- read.csv("../Data/1percent_flyModel2_counts.csv")
one_percent_manual <- read.csv("../Data/1percent_manualcounts.csv")

one_percent <- one_percent_manual %>% full_join(one_percent_model, join_by("FileName"))
```


```{r}
#versatile flow model
ggplot(data = one_percent, aes(x = Manual, y = Versatile_fluo)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
  theme_prism(base_size = 10) +
  xlab("Manual counts") +
  ylab("Model counts") +
  scale_x_continuous(limits = c(0,100), breaks = c(seq(0,100, by=20))) +
  scale_y_continuous(limits = c(0,100), breaks = c(seq(0,100, by=20))) + 
  theme(
    axis.text = element_text(size = 24),
    axis.title = element_text(size = 24)
  )

ggsave("../Results/versatile_fluo.pdf")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

